Writing News Captions with Bags of Attention

### 2019-10-21 paper/paper.tex
Add more citations

%%%%%%%%% ABSTRACT
\begin{abstract}
   In this work, we present an end-to-end captioning system for news articles
   that can handle entity names and out-of-vocabulary words. Our model achieves
   state-of-the-art results on the existing ``GoodNews" dataset. We also
   re-collected news articles from the New York Times, which are cleaner and
   more complete. This dataset allows us to explore approaches involving
   image positions. The code will be made available on GitHub.
\end{abstract}

@@

   \item We build on the “Good News” dataset to produce a larger and more complete
   news captioning dataset consisting of * articles from the New York Times and
   their 794K images with captions. In contrast to “Good News” our dataset
   contains the full article text, and the location of the image within the
   page.
\end{itemize}

@@

@@

\section{Results}

@@

\begin{table*}[t]
	\caption {Word statistics on the GoodNews test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.1 & 17.0 \\
      Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
      Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
      Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
      Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
      Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
      \midrule
      LSTM + GloVe & 13.9 & 11.4 \\
      LSTM + RoBERTa &  &  \\
      Transformer + GloVe & &  \\
      Transformer + RoBERTa & 15.7 & 13.8 \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
   We propose an end-to-end model to generate image captions in news articles.
   By combining the transformer architecture, byte-pair encoding, pretrained
   text and image embeddings, and bags of attentions, our system is able to
   describe an image using specific events and names mentioned in the article.
   Our model achieves state-of-the-art results on the existing GoodNews
   dataset. We also extend the GoodNews dataset to improve the quality of
   articles and study the importance of the image location on the page.
\end{abstract}

@@

   \item We build on the GoodNews dataset to produce a larger and more
   complete news captioning dataset consisting of 445,828 articles from the New
   York Times and their 794K images with captions. In contrast to GoodNews
   our dataset contains the full article text, and the location of the image
   within the page.
\end{itemize}

@@

We use MTCNN \cite{Zhang2016JointFD} to detect faces and FaceNet
\cite{Schroff2015FaceNetAU} trained on the VGGFace2 dataset
\cite{Cao2017VGGFace2AD}
to classify the faces.

@@

\section{Experiments}

The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
dynamic convolution code comes from fairseq \cite{Ott2019Fairseq}. The code
will made public on GitHub.

@@

\begin{table*}[t]
	\caption {Word statistics on the GoodNews test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.1 & 17.0 \\
      \midrule
      Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
      Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
      Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
      Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
      Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
      \midrule
      LSTM + GloVe & 13.9 & 11.4 \\
      LSTM + RoBERTa &  &  \\
      Transformer + GloVe & &  \\
      Transformer + RoBERTa & 15.7 & 13.8 \\
		\bottomrule
	\end{tabular}
\end{table*}
